Earth_microbiome_MS

### 2019-07-15 Earth_microbiome_MS.Rmd
updated

##Microbiome Data Import
```{r Microbiome Data Import}
#file.choose() has been chosen here to take away any errors pertaining to the file path while investigating the files from the ftp directory
githubdata_biom = file.choose()

#This function transforms a biom file into a phyloseq class object
githubdata_phyloseq = read_biom2phyloseq(githubdata_biom)

@@

@@

#Read phyloseq object
```{r OTU table read}

>>>>

##Microbiome Data Import
```{r Microbiome Data Import}
#file.choose() has been chosen here to take away any errors pertaining to the file path while investigating the files from the ftp directory
githubdata_biom <- file.choose()

#This function transforms a biom file into a phyloseq class object
githubdata_phyloseq <- read_biom2phyloseq(githubdata_biom)

@@

#ftpdata_silva_qrbiom = import_qiime("/Users/Muriel/globalmicrobiome/emp_cr_silva_16S_123qc_filtered.biom")
#ftpdata_silva_phyloseq = read_biom2phyloseq(ftpdata_silva_qrbiom)

@@

#Read phyloseq object
```{r Pseq read}
#Methods obtained from Callahan et al.

rank_names(githubdata_phyloseq)
